### 2016-03-14 ch03-lrm/LPMSmooth_ML_EG_JS_JL.tex
TODO
Some work on conclusion
Improve figures, short captions

\begin{figure}[tbh] %top bottom here
\centering
\setlength\figurewidth{0.85\columnwidth}
\setlength\figureheight{0.68\figurewidth}
% \includegraphics[scale=0.9]{\thisDir/figs/expFitest}
\input{\thisDir/figs/expfit.tikz}
\caption{Truncation of the impulse response via the fit of  an exponential. The light gray line is the noisy impulse response, and the dark gray one is its absolute value. Gray circles: monotonously decreasing maxima, greater than $5\hat\sigma$, as per \eqref{eq:TmaxDef}. Black thick line: estimated exponential function \eqref{eq:expFit}.}
\label{FRF_truncate_expfitter}
\end{figure}

@@

\begin{figure}[tbh] %top bottom here
    \centering
    \includegraphics[scale=0.9]{\thisDir/figs/figLPMvsTruncWlegend}
    \caption{Comparison of the \gls{LPM} and Truncated \gls{LPM} estimates of the \gls{FRF} for an \gls{SNR} of $18.3\unit{dB}$. The gray plots pertain to the \gls{LPM} estimate without truncation, the black ones to the \gls{LPM} with truncation (trunc). Dots: \gls{FRF} estimates $\hat{G}$. Crosses: sample standard deviations $\hat{\sigma}$. Dashed lines: bias $\hat{b}$. White line: the true system $G_0$.}
    \label{figLPMvsTrunc}
\end{figure}

@@

\begin{figure}[htb] %  figure placement: here, top, bottom, or page
   \centering
	\includegraphics{\thisDir/figs/HistogramExpFitting.pdf}
         \caption{Black full line (left hand side y-axis (ordinate)): total \gls{RMS} error as a function of the truncation time (the single black dot is the minimum of the \gls{RMS}). Gray histogram (right hand side y-axis (ordinate)): selected truncation times for 1000 noise realizations by the exponential fitting methods.}
   \label{fig:pdfAndRMSeVStruncTime}
\end{figure}

>>>>

\begin{figure}[tbh] %top bottom here
\centering
\setlength\figurewidth{0.85\columnwidth}
\setlength\figureheight{0.68\figurewidth}
% \includegraphics[scale=0.9]{\thisDir/figs/expFitest}
\input{\thisDir/figs/expfit.tikz}
\caption[Impulse response truncation using exponential fit.]{Truncation of the impulse response via the fit of  an exponential. 
The light gray line is the noisy impulse response, and the dark gray one is its absolute value. 
Gray circles: monotonously decreasing maxima, greater than $5\hat\sigma$, as per \eqref{eq:TmaxDef}. 
Black thick line: estimated exponential function \eqref{eq:expFit}.}
\TODO{describe marker again!}
\label{FRF_truncate_expfitter}
\end{figure}

@@

\begin{figure}[tbh] %top bottom here
    \centering
    \includegraphics[scale=0.9]{\thisDir/figs/figLPMvsTruncWlegend}
    \caption[Comparison of FRF estimated using LPM and Truncated LPM.]{Comparison of the \gls{LPM} and Truncated \gls{LPM} estimates of the \gls{FRF} for an \gls{SNR} of $18.3\unit{dB}$. The gray plots pertain to the \gls{LPM} estimate without truncation, the black ones to the \gls{LPM} with truncation (trunc). Dots: \gls{FRF} estimates $\hat{G}$. Crosses: sample standard deviations $\hat{\sigma}$. Dashed lines: bias $\hat{b}$. White line: the true system $G_0$.}
    \label{figLPMvsTrunc}
\end{figure}

@@

\begin{figure}[htb] %  figure placement: here, top, bottom, or page
   \centering
	\includegraphics{\thisDir/figs/HistogramExpFitting.pdf}
         \caption[RMS error of the FRF versus truncation time.]{Black full line (left hand side y-axis (ordinate)): total \gls{RMS} error as a function of the truncation time (the single black dot is the minimum of the \gls{RMS}). Gray histogram (right hand side y-axis (ordinate)): selected truncation times for 1000 noise realizations by the exponential fitting methods.}
   \label{fig:pdfAndRMSeVStruncTime}
\end{figure}

### 2016-03-14 ch05-initvals/initial-values.tex
Improve figures, short captions

\begin{figure}
  \centering
  \setlength{\figurewidth}{0.85\columnwidth}
  \setlength{\figureheight}{0.68\figurewidth}
  \input{\thisDir/fig/successRates.tikz}
 \caption[Simulated success rate of the different initialization schemes for varying \gls{SNR}.]{The success rate $\successRate$  obtained using the smoothers, i.e. $\model{RFIR}$~\legref{leg:success-RFIR} and $\model{trunc}$~\legref{leg:success-LPMTrunc}, are significantly higher than for the existing methods $\model{exist}$~\legref{leg:success-existing} in most of the studied range of \glspl{SNR}, number of samples and for both test systems. The $95\%$ confidence intervals~\eqref{eq:initvals:Binomial:CI} are indicated by bars.}
  \label{fig:successRateVS_SNR36N3dB}
\end{figure}

\begin{figure}
  \centering
  \setlength{\figurewidth}{0.66\columnwidth}
  \setlength{\figureheight}{0.68\figurewidth}
  \input{\thisDir/fig/RMSEvs_SNR36N3dB-ripple6.tikz}
 \caption[Simulated model \gls{RMSE} compared to rule-of-thumb.]{The accordance between the observed \gls{RMSE} of $\hat{G}_0$~\legref{leg:RMSE:delta:observed}(with $\pm2\sigma$ interval) and the rule-of-thumb~\eqref{eq:heur-RMSE}\legref{leg:RMSE:rule-of-thumb} shows how well $\model{\trueSymbol}$ approximates the true system $\true{G}$.
 In the bottom plot, the difference between both is shown.
 Consequently, it makes sense to examine the behavior of the models in terms of $\model{\trueSymbol}$ as long as this RMSE meets the user's requirements.}
  \label{fig:RMSE}
\end{figure}

@@

\begin{figure}
  \centering
  \setlength{\figurewidth}{0.75\columnwidth}
  \setlength{\figureheight}{0.68\figurewidth}
  \input{\thisDir/fig/elvis-spectra.tikz}
  %TODO: simplify figure
  \caption[Measured input/output spectra of \BK{} filter.]{Average input $\tilde{U}(\omega)$ and output $\tilde{Y}(\omega)$ spectra \legref[2]{leg:SpectraMeasurement:U:mean} measured using the Elvis and the noise levels $\hat\sigma_U$ and $\hat\sigma_Y$  \legref[2]{leg:SpectraMeasurement:U:noise}.}
  \label{fig:SpectraMeasurement}
\end{figure}

@@

\begin{figure}
  \centering
  \ref{leg:init:secondBest}
  \setlength{\figurewidth}{0.75\columnwidth}
  \setlength{\figureheight}{0.60\figurewidth}
  \input{\thisDir/fig/special-histogram.tikz}
  %TODO: put legend inside figure (note: subplot magic!!)
  \caption[Performance degradation/enhancement for selecting the second best model.]{
  Performance degradation/enhancement ($X_{\bullet}-X_{\mathrm{best}}$) for choosing a given method $\bullet$ instead of the `best' method for the measurement example in this chapter.
  The markers show individual observations and the boxes show the \gls{IQR}.
  The dashed lines are the minimum, median and maximum of $X_{\bullet}$ to give a sense of scale.
  On average there is little to gain or lose from using $\model{RFIR}$ instead of $\model{best}$.
  For $\model{exist}$ and $\model{trunc}$, the situation is a lot less favorable.
  }
  \label{fig:init:histogramEnhancement}
\end{figure}

>>>>

\begin{figure}
  \centering
  \setlength{\figurewidth}{0.85\columnwidth}
  \setlength{\figureheight}{0.68\figurewidth}
  \input{\thisDir/fig/successRates.tikz}
 \caption[Simulated success rate of the different initialization schemes for varying SNR.]{The success rate $\successRate$  obtained using the smoothers, i.e. $\model{RFIR}$~\legref{leg:success-RFIR} and $\model{trunc}$~\legref{leg:success-LPMTrunc}, are significantly higher than for the existing methods $\model{exist}$~\legref{leg:success-existing} in most of the studied range of \glspl{SNR}, number of samples and for both test systems. The $95\%$ confidence intervals~\eqref{eq:initvals:Binomial:CI} are indicated by bars.}
  \label{fig:successRateVS_SNR36N3dB}
\end{figure}

\begin{figure}
  \centering
  \setlength{\figurewidth}{0.66\columnwidth}
  \setlength{\figureheight}{0.68\figurewidth}
  \input{\thisDir/fig/RMSEvs_SNR36N3dB-ripple6.tikz}
 \caption[Simulated model RMSE compared to rule-of-thumb.]{The accordance between the observed \gls{RMSE} of $\hat{G}_0$~\legref{leg:RMSE:delta:observed}(with $\pm2\sigma$ interval) and the rule-of-thumb~\eqref{eq:heur-RMSE}\legref{leg:RMSE:rule-of-thumb} shows how well $\model{\trueSymbol}$ approximates the true system $\true{G}$.
 In the bottom plot, the difference between both is shown.
 Consequently, it makes sense to examine the behavior of the models in terms of $\model{\trueSymbol}$ as long as this RMSE meets the user's requirements.}
  \label{fig:RMSE}
\end{figure}

@@

\begin{figure}
  \centering
  \setlength{\figurewidth}{0.75\columnwidth}
  \setlength{\figureheight}{0.68\figurewidth}
  \input{\thisDir/fig/elvis-spectra.tikz}
  \caption[Measured input/output spectra of \BK{} filter.]{Average input $\tilde{U}(\omega)$ and output $\tilde{Y}(\omega)$ spectra \legref[2]{leg:SpectraMeasurement:U:mean} measured using the Elvis and the noise levels $\hat\sigma_U$ and $\hat\sigma_Y$  \legref[2]{leg:SpectraMeasurement:U:noise}.}
  \label{fig:SpectraMeasurement}
\end{figure}

@@

\begin{figure}
  \centering
  % \ref{leg:init:secondBest}
  \setlength{\figurewidth}{0.75\columnwidth}
  \setlength{\figureheight}{0.60\figurewidth}
  \input{\thisDir/fig/special-histogram.tikz}
  \caption[Performance degradation/enhancement for selecting the second best model.]{
  Performance degradation/enhancement ($X_{\bullet}-X_{\mathrm{best}}$) for choosing a given method $\bullet$ instead of the `best' method for the measurement example in this chapter.
  The markers show individual observations and the boxes show the \gls{IQR}.
  The dashed lines are the minimum, median and maximum of $X_{\bullet}$ to give a sense of scale.
  On average there is little to gain or lose from using $\model{RFIR}$ instead of $\model{best}$.
  For $\model{exist}$ and $\model{trunc}$, the situation is a lot less favorable.
  }
  \label{fig:init:histogramEnhancement}
\end{figure}
